Log or not - Analysis of ECDC forecasts

### 2022-01-31 analysis/Analysis ECDC forecasts.Rmd
update WIS-size simulation plot

```{r}
scores |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  ggplot(aes(y = interval_score, x = target_type)) + 
  geom_violin(aes(fill = target_type), alpha = 0.2, color = NA) + 
  geom_boxplot(alpha = 0.5) + 
  scale_fill_brewer(palette = "Set1", name = "Forecast target") + 
  facet_wrap(~ scale, scale = "free") + 
  theme_minimal() + 
  theme(legend.position = "none") + 
  scale_y_continuous(labels = scale_fn, trans = "log10") + 
  labs(y = "Interval score", x = "Target type")

ggsave("output/figures/HUB-average-scores.png", width = 7, height = 5)
```

@@

@@

  scores |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  group_by(target_type, location, scale) |>
  summarise(wis = summary_fct(interval_score), 
            .groups = "drop_last") |> 
  inner_join(total_values) |>
  ggplot(aes(y = wis, x = total)) + 
  geom_point() + 
  facet_wrap(~ target_type + scale, scale = "free") + 
  theme_minimal() + 
  theme(legend.position = "none") + 
  scale_x_continuous(labels = scale_fn) +
  scale_y_continuous(labels = scale_fn) +
  labs(y = "REPLACE", x = "Total number of observed values")
}

@@

>>>>

```{r}
scores |>
  dplyr::select(location, target_type, scale, target_end_date, interval_score) |>
  unique() |>
  group_by(target_type, scale) |>
  summarise(mean_value = mean(interval_score), 
            sd_value = sd(interval_score), 
            var_value = var(interval_score))

scores |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  ggplot(aes(y = interval_score, x = target_type)) + 
  geom_violin(aes(fill = target_type), alpha = 0.2, color = NA) + 
  geom_boxplot(alpha = 0.5) + 
  scale_fill_brewer(palette = "Set1", name = "Forecast target") + 
  facet_wrap(~ scale, scale = "free") + 
  theme_minimal() + 
  theme(legend.position = "none") + 
  scale_y_continuous(labels = scale_fn, trans = "log10") + 
  labs(y = "Interval score", x = "Target type")

ggsave("output/figures/HUB-average-scores.png", width = 7, height = 3.5)
```

@@

## Correlation between scores

```{r}
scores |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  group_by(target_type, location, scale) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") %>%
  pivot_wider(values_from = interval_score, names_from = scale) %>%
  group_by(target_type) %>%
  summarise(correlation = cor(natural, log))
```

@@

  plot_df <- scores |> 
    filter(model == "EuroCOVIDhub-ensemble", 
           horizon == 2) |>
    group_by(target_type, location, scale) |>
    summarise(wis = summary_fct(interval_score), 
              .groups = "drop_last") |> 
    inner_join(total_values)

  plot_df |>
    group_by(target_type, scale) |>
    summarise(correlation = cor(wis, total)) |> 
    print()

  plot_df |>
    ggplot(aes(y = wis, x = total)) + 
    geom_point() + 
    facet_wrap(~ target_type + scale, scale = "free") + 
    theme_minimal() + 
    theme(legend.position = "none") + 
    scale_x_continuous(labels = scale_fn) +
    scale_y_continuous(labels = scale_fn) +
    labs(y = "REPLACE", x = "Total number of observed values")
}

@@

# correlation
